Tampering Detection In Low-Power Smart Cameras

### 2015-05-20 paper.tex
aggiunti nuove ROC

\begin{abstract}
A desirable feature for smart cameras is the ability to autonomously detect any tampering event/attack that would prevent a clear view over the monitored scene. No matter whether tampering is due to atmospheric phenomena (e.g., few rain drops over the camera lens) or to malicious attack (e.g., the device displacement), these have to be promptly detected to possibly activate countermeasures. Tampering detection becomes particularly challenging in battery-powered cameras, where it is not possible to acquire images at video-like frame-rates, nor use sophisticated image-analysis algorithms.

@@

% Why is it interesting and important?
The early detection of tampering events/attacks is clearly essential in surveillance systems \gi{Adriano, add REFERENCES}, where cameras are expected to autonomously detect any tampering event/attack and promptly report alerts. Surveillance cameras are typically connected to the power supply and acquire and process images at normal frame-rates (e.g. around few frames per second). In these conditions, several algorithms have been presented in the literature \gi{Adriano add REFERENCES}.

@@

% Why is it hard? (E.g., why do naive approaches fail?)
Tampering detection in low-power smart cameras is much more challenging than in conventional surveillance cameras. Beside computational aspects -- such as the number of operations per pixels allowed -- the big issue is that low-power smart cameras typically operate at very low-frame rates (e.g., less than one frame per minute), and the acquired sequence does not evolve smoothly. This prevents the use of learned background models and the analysis of foreground variations \gi{REFERENCE su BKGR SUBTRACTION}. When dynamic environments are acquired at low frame rates, like the example depicted in Fig. \ref{fig:buenosAires}, two consecutive frames might be very different because of changes in the scene and in the light conditions: smart cameras have to correctly distinguish between these \emph{normal} changes and changes due to camera displacement or blur/defocus. Moreover, in low-power smart cameras, tampering has to be reliably detected because false alerts would lead to unnecessary energy waste.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{Immagini/ROCdefocus}
	\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens, while in Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens.}
	\label{fig:ROCdispl_luma}
\end{figure}

>>>>

\begin{abstract}
A desirable feature for smart cameras is the ability to autonomously detect any tampering event/attack that would prevents a clear view over the monitored scene. No matter whether tampering is due to atmospheric phenomena (e.g., few rain drops over the camera lens) or to malicious attack (e.g., the device displacement), these have to be promptly detected to possibly activate countermeasures. Tampering detection becomes particularly challenging in battery-powered cameras, where it is not possible to acquire images at video-like frame-rates, nor use sophisticated image-analysis algorithms.

@@

% Why is it interesting and important?
The early detection of tampering events/attacks is clearly essential in surveillance systems \gi{Adriano, add REFERENCES} \cite{hampapur2005smart}, where cameras are expected to autonomously detect any tampering event/attack and promptly report alerts. Surveillance cameras are typically connected to the power supply and acquire and process images at normal frame-rates (e.g. around few frames per second). In these conditions, several algorithms have been presented in the literature \gi{Adriano add REFERENCES}.

@@

% Why is it hard? (E.g., why do naive approaches fail?)
Tampering detection in low-power smart cameras is much more challenging than in conventional surveillance cameras \cite{perrig2004security}. Beside computational aspects -- such as the number of operations per pixels allowed -- the big issue is that low-power smart cameras typically operate at very low-frame rates (e.g., less than one frame per minute), and the acquired sequence does not evolve smoothly. This prevents the use of learned background models and the analysis of foreground variations \gi{REFERENCE su BKGR SUBTRACTION}. When dynamic environments are acquired at low frame rates, like the example depicted in Fig. \ref{fig:buenosAires}, two consecutive frames might be very different because of changes in the scene and in the light conditions: smart cameras have to correctly distinguish between these \emph{normal} changes and changes due to camera displacement or blur/defocus. Moreover, in low-power smart cameras, tampering has to be reliably detected because false alerts would lead to unnecessary energy waste.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{Immagini/ROCdefocus1}
	\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens, while in Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens.}
	\label{fig:ROCdispl_luma}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{Immagini/ROCdefocus_fd}
	\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens, while in Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens.}
	\label{fig:ROCdispl_luma}
\end{figure}
